%%
%% This is file `thesis-ex.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% uiucthesis2014.dtx  (with options: `example')
%% 
\def\fileversion{v2.25b} \def\filedate{2017/05/02}
%% Package and Class "uiucthesis2014" for use with LaTeX2e.
\documentclass[12pt,edeposit,fullpage]{uiucthesis2014}

% references at the end of each chapter
\usepackage[round,sectionbib]{natbib}
\usepackage{chapterbib}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bibentry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{rotating}

\def\aap{{A\&A}}
\def\AaA{{A\&A}}
\def\AJ{{AJ}}
\def\aj{{AJ}}
\def\ApJ{{ApJ}}
\def\apj{{ApJ}}
\def\apjl{{ApJL}}
\def\ApJL{{ApJL}}
\def\ApJSupp{{ApJS}}
\def\MN{{MNRAS}}
\def\mnras{{MNRAS}}
\def\mnrasl{{MNRAS Letters}}
\def\pasp{{PASP}}
\def\jcap{JCAP}
\def\pasj{{PASJ}}
\def\nat{Nature}
\def\ARAA{{ARA\&A}}
\def\apjs{{ApJS}}
\def\araa{{ARA\&A}}
\def\apss{{Ap\&SS}}
\def\cjaa{{ChJAA}}
\def\aaps{{A\&AS}}

\newcommand{\eg}{{e.g., }}
\newcommand{\ie}{{i.e., }}
\newcommand\blfootnote[1]{%
  \begingroup
  \renewcommand\thefootnote{}\footnote{#1}%
  \addtocounter{footnote}{-1}%
  \endgroup
}

% put figure on a new page
\renewcommand{\floatpagefraction}{0.1}

\nocopyrightpage

\begin{document}

\title{Machine Learning Approaches to\\
       Star-galaxy Classification}
\author{Junhyung Kim}
\department{Physics}
\phdthesis
\advisor{Robert J.\ Brunner}
\degreeyear{2018}
\committee{
    Professor Emeritus Jon J.\ Thaler, Chair\\
    Professor Robert J.\ Brunner, Director of Research\\
    Professor George D.\ Gollin\\
    Assistant Professor Alexander G.\ Schwing}
\maketitle

\frontmatter

%% Create an abstract that can also be used for the ProQuest abstract.
%% Note that ProQuest truncates their abstracts at 350 words.
\begin{abstract}
Accurate star-galaxy classification has many important applications in modern precision cosmology.
However, a vast number of faint sources that are detected in the current and
next-generation ground-based surveys may be challenged by poor star-galaxy classification.
Thus, we explore a variety of machine learning approaches to improve
star-galaxy classification in ground-based photometric surveys.
In Chapter~\ref{chapter2}, we present a meta-classification framework that combines existing star-galaxy classifiers,
and demonstrate that our Bayesian combination technique improves the overall performance over any individual classification method.
In Chapter~\ref{chapter3}, we show that a deep learning algorithm called convolutional neural networks
is able to produce accurate and well-calibrated classifications by learning directly from the pixel values of photometric images.
In Chapter~\ref{chapter4}, we study another deep learning technique called generative adversarial networks
in a semi-supervised setting, and demonstrate that our semi-supervised method produces competitive classifications
using only a small amount of labeled examples.

\end{abstract}

%% Create a dedication in italics with no heading, centered vertically
%% on the page.
%\begin{dedication}
%To Father and Mother.
%\end{dedication}

%% Create an Acknowledgements page, many departments require you to
%% include funding support in this.
\chapter*{Acknowledgments}

First and formorest, I would like to thank my advisor, Robert Brunner, for his guidance and support
during my graduate studies at UIUC.
I also wish to thank my committee members, Jon Thaler, George Gollin, and Alex Schwing, for their help and support.
I am also grateful to Matias Carrasco Kind, Yiran Wang, Nacho Sevilla, William Biscarri, Samantha Thrush, Xinyang Lu, and Kelechi Ikegwu.
A special thanks to my father and my wife who endured this long process with me.

\begin{flushright}
--- Edward Junhyung Kim
\end{flushright}

\vspace{10mm}

This work was supported in part by the National Science Foundation Grant
No.\ AST-1313415.
This work used the Extreme Science and Engineering Discovery Environment
(XSEDE), which is supported by National Science Foundation grant number
ACI-1053575.
This work is based on observations obtained with MegaPrime/MegaCam, a
joint project of CFHT and CEA/DAPNIA, at the Canada-France-Hawaii
Telescope (CFHT) which is operated by the National Research Council
(NRC) of Canada, the Institut National des Sciences de l'Univers of
the Centre National de la Recherche Scientifique (CNRS) of France, and
the University of Hawaii. This research used the facilities of the
Canadian Astronomy Data Centre operated by the National Research
Council of Canada with the support of the Canadian Space Agency.
CFHTLenS data processing was made possible thanks to significant
computing support from the NSERC Research Tools and Instruments grant
program.
Funding for the DEEP2 survey has been provided by NSF grants AST-0071048,
AST-0071198, AST-0507428, and AST-0507483. 
Funding for SDSS-III has been provided by the Alfred P. Sloan Foundation, the
Participating Institutions, the National Science Foundation, and the U.S.
Department of Energy Office of Science. The SDSS-III web site is
http://www.sdss3.org/.
This work used data from the 
VIMOS Public Extragalactic Redshift Survey (VIPERS).
VIPERS has been performed using the ESO Very Large Telescope, under the "Large
Programme" 182.A-0886. The participating institutions and funding agencies are
listed at http://vipers.inaf.it/.
This work used data from the VIMOS VLT Deep Survey, obtained from the VVDS
database operated by Cesam, Laboratoire d'Astrophysique de Marseille, France.

%% The thesis format requires the Table of Contents to come
%% before any other major sections, all of these sections after
%% the Table of Contents must be listed therein (i.e., use \chapter,
%% not \chapter*).  Common sections to have between the Table of
%% Contents and the main text are:
%%
%% List of Tables
%% List of Figures
%% List Symbols and/or Abbreviations
%% etc.

\tableofcontents
%\listoftables
%\listoffigures

%% Create a List of Abbreviations. The left column
%% is 1 inch wide and left-justified
%\chapter{List of Abbreviations}
%
%\begin{symbollist*}
%\item[CA] Caffeine Addict.
%\item[CD] Coffee Drinker.
%\end{symbollist*}

%% Create a List of Symbols. The left column
%% is 0.7 inch wide and centered
%\chapter{List of Symbols}
%
%\begin{symbollist}[0.7in]
%\item[$\tau$] Time taken to drink one cup of coffee.
%\item[$\mu$g] Micrograms (of caffeine, generally).
%\end{symbollist}

\mainmatter

\include{1-introduction}
\include{2-kim2015hybrid}
\include{3-kim2017star}
\include{4-kim2017ssgan}
\include{5-conclusion}

%\appendix*
%\include{Appendix.tex}

\backmatter

%\bibliographystyle{plainnat}
%\bibliography{thesisbib}

\end{document}
\endinput
%%
